### 2019-08-06 thesis.tex
*** empty log message ***

Since the pervasiveness of the plasma state in space came as a fact, plasma
physics became an essential component in the multidisciplinary framework of
astrophysics \cite{Alfven1950,Parker1956,Alfven1961,Gailitis1964}. At the
same time, the analysis and interpretation of observational data have been
gaining increasing relevance in the progress of theoretical, computational,
and experimental plasma physics research \cite{YZKS16,Donnert2014,Pezzi2018,
  Howes2018,Peterson2019}. This interconnection between plasma physics and
astrophysics was scrutinized by Hannes Alfvén, 1970's Nobel prize winner
plasma physicist, in a Physics Today's article \cite{Alfven1971} in 1971.

% Since the ubiquity of plasmas in space came as a fact, astrophysicists and
% plasma physicists have been noticing an increasing necessity for exchanging
% knowledge and mutually collaborating with their results. A particular field
% of research that has been acting for a long time as a bridge between these two
% areas is the solar physics. The accessibility of the solar plasma to direct,
% in siztu measurements, highly resolved remote sensing and high-resolution
% spectroscopy turned the solar system into Earth's space physics laboratory.

% The absolute majority of the plasma observed in space is far away from us,
% being accessible only through analysis of the electromagnetic spectrum
% emitted from their quite remote location. A fortunate exception to this
% fact is the plasma in our solar system.

>>>>

As soon as the pervasiveness of the plasma state in space came as a fact,
plasma physics began to be recognized as an essential component in the
multidisciplinary framework of astrophysics \cite{Alfven1950,Parker1956,
  Alfven1961,Gailitis1964,Alfven1971}. At the same time, the analysis and
interpretation of observational data started to have increasing relevance
in the progress of theoretical, computational, and experimental plasma
physics research \cite{YZKS16,Donnert2014,Pezzi2018,Howes2018,Peterson2019}.
In this context of mutual collaboration, the solar and interplanetary
plasma research has a pivotal contribution. The accessibility to direct,
in situ measurements, highly resolved remote sensing and high-resolution
spectroscopy, turned the solar system into a space plasma laboratory.
Processes like magnetic reconnection, particle acceleration, shocks, and
turbulence can be "closely" observed by space probes, and the understanding
acquired may be extended or adapted to address similar phenomena observed
in remote astrophysical environments \cite{NAP10477}.

The analysis presented in this doctoral thesis was analyzed in the context
of solar physics. 
% In this appendix we present a brief discussion on the current state-of-art
% solar physics and
